Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-10-13 Manuscript/manuscript.tex
Small update to methods - scaling of POPS - where and why

In the case of POPS, which is a monovalently negatively charged lipid, 
we used exactly this scaling factor 
to represent the effects of electronic polarization
yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}

@@

>>>>

@@

In the case of POPS, which is a monovalently negatively charged lipid, 
we used exactly the pre-determined scaling factor 
to represent the effects of electronic polarization
yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
Similarly to the ECC-POPC model, we changed the charges only of the polar parts of the phospholipid,
i.e., charges on all atoms except on alkyl tails, 
which do not encounter direct contacts with ions.
